R Notebook

### 2022-01-31 Code/Simulation.Rmd
Fixed bins in histograms

# Create the histograms displaying p-values from each test
hist1 <- suppressWarnings(test_rounded(10000, 10000, 4))
hist2 <- suppressWarnings(test_rounded(10000, 10000, 3))
hist3 <- suppressWarnings(test_rounded(10000, 10000, 2))
hist4 <- suppressWarnings(test_rounded(10000, 10000, 1))

@@

# Generate histograms plot
hist_rounded <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
```

@@

      # Generate random correlated data, perform a KS-test, and store the p-value
      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 500)
      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = ars[i])
    }
  }

@@

# Generate histograms plot
hist_correlation <- ggplot(ar_results, aes(x = p_value)) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~ar, scales = "free_y", ncol = 3)
```

@@

# Create the histograms displaying p-values from each test
test1 <- suppressWarnings(test_dgof(10000, 30, 3))
test2 <- suppressWarnings(test_dgof(10000, 30, 2))
test3 <- suppressWarnings(test_dgof(10000, 30, 1))
results <- rbind(test1, test2, test3)

# Generate histograms plot
hist_dgof <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 3, scales = "free_y")
```

@@

# Generate histograms plot
hist_dgofsim <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, scales = "free_y")
```

```{r}
# Test parametric bootstrap as a solution to fitting parameters
test_parametric <- function(x, B = 200) {

@@

# Generate results
pvals_parametric <- replicate(1000, test_parametric(rnorm(100), B = 200)$p.value)
pvals_naive <- replicate(1000, test_naive(rnorm(100))$p.value)

@@

# Generate histograms plot
hist_parametric <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")

@@

```{r}
ggsave(filename="hist_normal.pdf", plot=hist_normal, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_rounded.pdf", plot=hist_rounded, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_correlation.pdf", plot=hist_correlation, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_dgof.pdf", plot=hist_dgof, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_dgofsim.pdf", plot=hist_dgofsim, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_parametric.pdf", plot=hist_parametric, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
```

>>>>

# Create the histograms displaying p-values from each test
hist1 <- suppressWarnings(test_rounded(10000, 100, 4))
hist2 <- suppressWarnings(test_rounded(10000, 100, 3))
hist3 <- suppressWarnings(test_rounded(10000, 100, 2))
hist4 <- suppressWarnings(test_rounded(10000, 100, 1))

@@

# Generate histograms plot
hist_rounded <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value") + facet_wrap(.~histogram, scales = "free_y")
```

@@

      # Generate random correlated data, perform a KS-test, and store the p-value
      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 100)
      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = ars[i])
    }
  }

@@

# Generate histograms plot
hist_correlation <- ggplot(ar_results, aes(x = p_value)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~ar, scales = "free_y", ncol = 3)
```

@@

# Create the histograms displaying p-values from each test
test1 <- suppressWarnings(test_dgof(10000, 100, 3))
test2 <- suppressWarnings(test_dgof(10000, 100, 2))
test3 <- suppressWarnings(test_dgof(10000, 100, 1))
results <- rbind(test1, test2, test3)

# Generate histograms plot
hist_dgof <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 3, scales = "free_y")
hist_dgof
```

@@

# Generate histograms plot
hist_dgofsim <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, scales = "free_y")
```

```{r}
# Split sample size into blocks, apply bootstrap onto blocks. Use that as x.b. Fit, stat.b
# Test parametric bootstrap as a solution to fitting parameters
test_parametric <- function(x, B = 1000) {

@@

# Generate results
pvals_parametric <- replicate(1000, test_parametric(rnorm(100), B = 1000)$p.value)
pvals_naive <- replicate(1000, test_naive(rnorm(100))$p.value)

@@

# Generate histograms plot
hist_parametric <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")

@@

```{r}
ggsave(filename="hist_normal.pdf", plot=hist_normal, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_rounded.pdf", plot=hist_rounded, path = "/Users/anthony//KS-Test-Thesis/Manuscript")
ggsave(filename="hist_correlation.pdf", plot=hist_correlation, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_dgof.pdf", plot=hist_dgof, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_dgofsim.pdf", plot=hist_dgofsim, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
ggsave(filename="hist_parametric.pdf", plot=hist_parametric, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
```
